NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-25 ms_nihao_budget.tex
first version of the draft for the second referee's comments

\documentclass[useAMS,usenatbib]{mn2e}
\input psfig.sty
\usepackage{array}
%\usepackage{graphicx}
%\usepackage{epstopdf}

@@

As might be expected, haloes with the highest masses we study have
high baryon fractions with relatively  small scatter. As halo mass
decreases, the baryon fraction decreases and the scatter increases,
consistent with expectations from outflows driven by stellar
feedback. At the lowest halo masses we study, below $10^{10}\Msun$,
the scatter starts to decrease. By contrast the scatter in the stellar
mass fraction increases below this scale. Thus it seems unlikely that
stellar feedback is primarily responsible for the low baryon
fractions.  Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. 
{\bf Although the three most massive galaixes in NIHAO suite have fairly 
high stellar masses (see blue filled circles in Fig.~\ref{fig:budget}),
they don't have large deviations apart from the fitting baryon fraction, 
and in the comparason with FIRE (see Fig.~\ref{fig:fire_com}), these
three objects seem to hint the trend on massive galaxy end associated
with the data from \citet{Voort16}. Moreover, the fitting relation 
about the baryon fraction is not sensitive to these three most massive 
galaxies as well since they have equal weight with other more than 
80 galaxies to shape the fitting curve.}

@@

\begin{itemize}
\item All of the NIHAO haloes have a lower baryon to dark matter ratio, 
      inside the virial radius, than the cosmic baryon fraction.

@@

\item The missing baryons from all haloes are located beyond 2 virial radii.

@@

\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ our
      simulations are consistent with the observed  fractions of stars,
      cold gas, warm and hot gas.

\item For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
      which is significantly lower than the observations from COS-HALOs
      ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
      analysis of \citet{Stern16}.

@@

We thank the anonymous referee whose suggestions greatly 
improve the paper.
{\sc Gasoline} was written by Tom Quinn and James Wadsley. Without
their contribution, this paper would have been impossible.
%
The simulations were performed on the {\sc theo} cluster of the
Max-Planck-Institut f\"ur Astronomie and the {\sc hydra} cluster at
the Rechenzentrum in Garching; and the Milky Way supercomputer, funded
by the Deutsche Forschungsgemeinschaft (DFG) through Collaborative
Research Center (SFB 881) "The Milky Way System" (subproject Z2),
hosted and co-funded by the J\"ulich Supercomputing Center (JSC). We
greatly appreciate the contributions of all these computing
allocations.
%
AAD, GSS and AVM acknowledge support through the
Sonderforschungsbereich SFB 881 “The Milky Way System” (subproject A1)
of the German Research Foundation (DFG).  The analysis made use of the
pynbody package \citep{Pontzen13}.
%
The authors acknowledge support from the MPG-CAS through the
partnership programme between the MPIA group lead by AVM and the PMO
group lead by XK.
%
LW acknowledges support of the MPG-CAS student programme.
%
XK acknowledge the support from 973 program (No. 2015CB857003,
2013CB834900), NSFC project No.11333008 and the ``Strategic Priority
Research Program the Emergence of Cosmological Structures'' of the
CAS(No.XD09010000).

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\input psfig.sty
\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage{epstopdf}

@@

As might be expected, haloes with the highest masses we study have
high baryon fractions with relatively  small scatter. As halo mass
decreases, the baryon fraction decreases and the scatter increases,
consistent with expectations from outflows driven by stellar
feedback {\bf since the energy-driven wind model determined that
mass loading factors show a power-law dependency on circular velocity
, with an exponent of $\approx -2$, \eg \citet{Christensen16}, 
which means the greater efficiency of small galaxies at 
driving outflows is simply a result of their shallower potential 
well and the increasing scatters come from the increasing scatters of
stellar mass halo mass relation in lower mass range.}
At the lowest halo masses we study, below $10^{10}\Msun$,
the scatter starts to decrease. By contrast the scatter in the stellar
mass fraction increases below this scale. Thus it seems unlikely that
stellar feedback is primarily responsible for the low baryon
fractions.  Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes. 
{\bf Although the three most massive galaixes in NIHAO suite have fairly 
high stellar masses (see blue filled circles in Fig.~\ref{fig:budget}),
they don't have large deviations apart from the fitting baryon fraction, 
and in the comparason with FIRE (see Fig.~\ref{fig:fire_com}), these
three objects seem to hint the trend on massive galaxy end associated
with the data from \citet{Voort16}. Moreover, the fitting relation 
about the baryon fraction is not sensitive to these three most massive 
galaxies as well since they have equal weight with other more than 
80 galaxies to shape the fitting curve.}

@@

\begin{itemize}
\item All of the NIHAO haloes have a lower baryon to dark matter ratio, 
      inside the virial radius, than the cosmic baryon fraction. 
      {\bf Higher fractions of baryons are lost as the virial mass 
      decreases in the mass range of $\lesssim 10^{12} \Msun$.
      The trend confirmed with \citet{Christensen16} and \citet{Voort16},
      and associated by \citet{Voort16}, the trend at higher mass range
      may suggest the baryon fraction is reduced larger as virial mass
      increase. }

@@

\item {\bf All haloes have less baryons than baryon mass derived by cosmic
       baryonic fraction even beyond 2 virial radii. The total 
       baryons derived by cosmic baryonic fraction within virial radius 
       can expand more than $8\Rvir$ for low mass haloes but less than
       $2\Rvir$ for high mass haloes.}

@@

\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ our
      simulations are consistent with the observed  fractions of stars,
      cold gas, warm and hot gas \citep{Werk14}. {\bf \citet{Peeples14} 
      showed a conservative observational estimate for warm-hot gas 
      which is lower limit of the result from \citet{Werk14} and the 
      warm-hot fraction from our study is well within the range of less
      conservative estimates.}

\item For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
      which is significantly lower than the observations from COS-HALOs
      ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
      analysis of \citet{Stern16}.
      {\bf As in \citet{Colin16}, the simulations suggest that the
      fraction of cool gas is approximately 10\%.}

@@

We thank the two anonymous referees whose suggestions greatly 
improve the paper.
{\bf We thank Freeke van de Voort for kindly sharing data of the FIRE
simulation.}
{\sc Gasoline} was written by Tom Quinn and James Wadsley. Without
their contribution, this paper would have been impossible.
%
The simulations were performed on the {\sc theo} cluster of the
Max-Planck-Institut f\"ur Astronomie and the {\sc hydra} cluster at
the Rechenzentrum in Garching; and the Milky Way supercomputer, funded
by the Deutsche Forschungsgemeinschaft (DFG) through Collaborative
Research Center (SFB 881) "The Milky Way System" (subproject Z2),
hosted and co-funded by the J\"ulich Supercomputing Center (JSC). We
greatly appreciate the contributions of all these computing
allocations.
%
AAD, GSS and AVM acknowledge support through the
Sonderforschungsbereich SFB 881 “The Milky Way System” (subproject A1)
of the German Research Foundation (DFG).  The analysis made use of the
pynbody package \citep{Pontzen13}.
%
The authors acknowledge support from the MPG-CAS through the
partnership programme between the MPIA group lead by AVM and the PMO
group lead by XK.
%
LW acknowledges support of the MPG-CAS student programme.
%
XK acknowledge the support from 973 program (No. 2015CB857003,
2013CB834900), NSFC project No.11333008 and the ``Strategic Priority
Research Program the Emergence of Cosmological Structures'' of the
CAS(No.XD09010000).
